Verifying Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
small shortening at start of sec 2

We first set up various definitions used in this paper.
\S~\ref{sec:syntax} then outlines the syntax of stencil specifications
and gives an informal introduction. \S~\ref{sec:semantics} then
gives a semantic model via a set-based interpretation which makes
concrete the meaning of specifications. \S~\ref{sec:eqs} then provides
a syntactic equational theory for specifications which is
sound with respect to the model.
%sub-specification for which the
%equality and sub-specification relation are proven sound.

\paragraph{Notation and convention}
%\label{sec:notation}

>>>>

We give various definitions used in the paper then 
\S~\ref{sec:syntax} outlines the syntax of stencil specifications
with an informal introduction. \S~\ref{sec:semantics} 
gives a semantic model via a set-based interpretation which makes
concrete the meaning of specifications. \S~\ref{sec:eqs} then provides
a syntactic equational theory for specifications which is
sound with respect to the model.
%sub-specification for which the
%equality and sub-specification relation are proven sound.

\paragraph{Notation}
%\label{sec:notation}
